### 2023-04-16 paper/language.tex
Preserve type information in PikaCore for use in later stages

The syntactic form that introduces an SSL assertion in \PikaCore{} can be seen as a kind of binding
form, the values of which can be ``applied''. For example, $\sslmath{x, y}{x \mapsto y, (x+1) \mapsto z}$
can be seen as an SSL assertion that is parametrized over two locations: $x$ and $y$. Also, the name
$z$ occurs free. When this layout value is applied to two locations, $z$ must remain a fresh variable in
the use-site.

@@

\begin{align*}
  &f\; \{ x \mapsto a \} := \sslmath{y, z}{(y+1) \mapsto a, z \mapsto w}
\end{align*}

@@

\begin{align*}
  &i ::= \cdots \mid -2 \mid -1 \mid 0 \mid 1 \mid 2 \mid \cdots
  \\
  &b ::= \True{} \mid \False
  \\
  &e ::= x \mid i \mid b \mid \lambda x.\; e
  \\
  &\tau ::= \Int \mid \Bool \mid \tau \ra \tau
\end{align*}

\subsection{\Pika{} Syntax}
\begin{align*}
  &e ::= \cdots \mid \apply_{\alpha}(e) \mid \Lambda (\alpha \isA \layout{X}).\; e
  \\
  &\tau ::= \cdots \mid X \mid \alpha \mid e\; e \mid (\alpha \isA \layout{X}) \Ra \tau
\end{align*}

\subsection{\PikaCore{} Syntax}
\begin{align*}
  &e ::= \cdots \mid e\; \overline{a} \mid \sslmath{\overline{x}}{\overline{h}} \mid \withIn{\{ \overline{x} \} := e} e
  \\
  &a ::= \{ \overline{x} \} \mid \{ i \} \mid \{ b \}
  \\
  &\tau ::= \cdots \mid \SSL(n)
  \\
  &h ::= \ell \mapsto e
  \\
  &\ell ::= x \mid (x + n)
  \\
  &n ::= 0 \mid 1 \mid 2 \mid \cdots
\end{align*}

The construct $\sslmath{\overline{x}}{\overline{h}}$ is an SSL assertion with heaplets $\overline{h}$ and
bound variables $\overline{x}$. Note that it can have free variables as well.

>>>>

The syntactic form that introduces an SSL assertion in \PikaCore{} can be seen as a kind of binding
form, the values of which can be ``applied''. For example, $\sslmath{x, y}{T}{x \mapsto y, (x+1) \mapsto z}$
can be seen as an SSL assertion that is parametrized over two locations: $x$ and $y$. Also, the name
$z$ occurs free. When this layout value is applied to two locations, $z$ must remain a fresh variable in
the use-site.

@@

\begin{align*}
  &f\; \{ x \mapsto a \} := \sslmath{y, z}{T}{(y+1) \mapsto a, z \mapsto w}
\end{align*}

@@

\begin{align*}
  &i ::= \cdots \mid -2 \mid -1 \mid 0 \mid 1 \mid 2 \mid \cdots
  \\
  &b ::= \True{} \mid \False
  \\
  &e ::= x \mid i \mid b \mid \lambda x.\; e
  \\
  &\tau ::= \Int \mid \Bool \mid \alpha \mid \tau \ra \tau
\end{align*}

\subsection{\Pika{} Syntax}
\begin{align*}
  &e ::= \cdots \mid \apply_{\alpha}(e) \mid \Lambda (\alpha \isA \Layout{X}).\; e
  \\
  &\tau ::= \cdots \mid X \mid e\; e \mid (\alpha \isA \Layout{X}) \Ra \tau
\end{align*}

\subsection{\PikaCore{} Syntax}
\begin{align*}
  &e ::= \cdots \mid e\; \overline{a} \mid \sslmath{\overline{x}}{T}{\overline{h}} \mid \withIn{\{ \overline{x} \} := e} e
  \\
  &a ::= \{ \overline{x} \} \mid \{ i \} \mid \{ b \}
  \\
  &\tau ::= \cdots \mid A
  \\
  &h ::= \ell \mapsto e
  \\
  &T ::= \overline{\ell : \tau}
  % \\
  % &d ::= \recspec{\overline{n : \tau}}
  \\
  &\ell ::= x \mid (x + n)
  \\
  &n ::= 0 \mid 1 \mid 2 \mid \cdots
\end{align*}

The construct $\sslmath{\overline{x}}{T}{\overline{h}}$ is an SSL assertion with heaplets $\overline{h}$ and
bound variables $\overline{x}$. Note that it can have free variables as well.

$\mu\alpha.\; \SSL(\overline{x : \tau})$ is an equi-recursive type, with $\mu$ being the recursive binder,
introducing the type variable $\alpha$. When
the variable bound by $\mu$ does not appear in any of the $\tau$, we leave out the binder and write $\SSL(\overline{x : \tau})$
as a shorthand.

% $d$ is a record specification, given by index. Consider the following SSL assertion.
% \[
%   \sslmath{x,y}{x \mapsto 1, (x+2) \mapsto \True, y \mapsto 22, (y+1) \mapsto 0}
% \]
% This could have the type $\SSL(x : \recspec{0 : \Int, 2 : \Bool}, y : \recspec{0 : \Int, 1 : \Int})$.
% It could have other types as well, however. For example, $y$ could also fit the
% layout of a singly-linked list. We might not know at a type-level how long a list is. So, the
% assertion also has the type
% $\SSL(x : \recspec{0 : \Int, 2 : \Bool}, y : \recspec{0 : \Layout})$. We use $\Layout$ to indicate
% that we only know

% $d$ is a record specification, given by index. Consider the following SSL assertion.
% \[
%   \sslmath{x,y}{x \mapsto 1, (x+2) \mapsto \True, y \mapsto 22, (y+1) \mapsto 0}
% \]
% This could have the type $\SSL(x : \recspec{0 : \Int, 2 : \Bool}, y : \recspec{0 : \Int, 1 : \Int})$.
% It could have other types as well, however. For example, $y$ could also fit the
% layout of a singly-linked list. If we have such a singly-linked list layout
% named \verb|Sll|, then the assertion would also have the type
% $\SSL(x : \recspec{0 : \Int, 2 : \Bool}, y : \recspec{0 : \texttt{Sll}})$. Regarding $y$, this
% type says that, at offset $0$, $y$ satisfies the \texttt{Sll} layout.
